Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
kill orphans MUAHHAH and making space

There are still many features of Tor that are left unevaluated through user research---such as advanced web tasks (such as accessing hidden services), the configuration menu to connect to the Tor network, configuring for automatic updates, and identity/cookie management. Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
Internet censorship is shown to be pervasive across the world today \cite{faris2008measuring}, with 
some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool.

@@

\noindent {\bfseries Experiment Flow} 
We will run three sets of the experiment, the first set to test the current configuration
interface, a second set to test the improved interface, and a third set to test the 
alternate configuration interface. The experiment flow will be the same across all 
sets of experiments, with the fact that the configuration interface will be altered 
across sets.

The experiment begins with the participants being informed that they are in a
simulated censorship
environment, where some --- but not all --- websites are blocked. We will
instruct them to visit a non-blocked website and a blocked website on a
``standard'' browser (one that is not used for censorship circumvention, such
as Chrome, Safari, or Firefox) to illustrate the situation.
Then, the participants will find out the role they they will be playing in the study.
This role is that of a regular citizen, who is trying to visit blocked websites
for non-critical leisurely purposes,
and that there is a minimal chance of risk. This information is given
to achieve
consistency across participants: their behavior might be different if they were
visiting websites to accomplish a critical task, or if they knew that there
were great risks.

@@

The experiment will conclude with a debriefing, which will inform that the
participants of their screen capture and obtaining re-consent for the
information.  \\

@@

% from anonymity study
Our online artifacts of study of Tor as an anonymity tool, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
\end{itemize}

>>>>

There are still many features of Tor that are left unevaluated through user research---such as advanced web tasks (such as accessing hidden services), the configuration menu to connect to the Tor network, configuring for automatic updates, and identity/cookie management. Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
Internet censorship is shown to be pervasive across the world today \cite{faris2008measuring}, with 
some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

@@

\noindent {\bfseries Experiment Flow} 
We will run three sets of the experiment, the first set to test the current configuration
interface, a second set to test the improved interface, and a third set to test the 
alternate configuration interface. The experiment flow will be the same across all 
sets of experiments, but the configuration interface will be different across sets.

The experiment begins with the participants being informed that they are in a
simulated censorship
environment, where some --- but not all --- websites are blocked. We will
instruct them to visit a non-blocked website and a blocked website on a
``standard'' browser (one that is not used for censorship circumvention, such
as Chrome, Safari, or Firefox) to illustrate the situation.
Then, the participants will find out the role they they will be playing in the study.
This role is that of a regular citizen, who is trying to visit blocked websites
for non-critical leisurely purposes,
and that there is a minimal chance of risk. This information is given
to achieve
consistency across participants: behaviors may change if the tasks were 
critical or if there were great risks associated with configuration mistakes.

@@

The experiment will conclude with a debriefing, which will inform that the
participants of their screen capture and obtaining re-consent for the
information.

@@

% from anonymity study
%Our online artifacts of study of Tor as an anonymity tool, such as 
%the summary, results, and resulting browser changes are below:
%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
%\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
%\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
%\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
%\end{itemize}
